Supplemental Information

### 2021-12-14 manuscript/supplement.Rmd
final changes to manuscript before initial submission

author:
- Courtney A. Copeland: 
    institute: 1
- Benjamin A. Olenchock: 
    institute: 1, 2
- David R. Ziehr:
    institute: 1, 4
- Sarah McGarrity: 
    institute: 1, 5
- Jamey D. Young: 
    institute: 3
- Joseph Loscalzo: 
    institute: 1
- William M. Oldham: 
    institute: 1
    email: woldham@bwh.harvard.edu
    correspondence: true
institute:
- 1: Department of Medicine, Brigham and Women's Hospital and Harvard Medical School, Boston, MA
- 2: Regeneron Pharmaceuticals, Tarrytown, NY
- 3: Departments of Chemical & Biomolecular Engineering and Molecular Physiology & Biophysics, Vanderbilt University, Nashville, TN
- 4: Department of Medicine, Massachusetts General Hospital and Harvard Medical School, Boston, MA
- 5: Center for Systems Biology, School of Health Sciences, University of Iceland, Reykjavik, Iceland

>>>>

author:
- Courtney A. Copeland: 
    institute: 1
- Benjamin A. Olenchock: 
    institute: 1
- David R. Ziehr:
    institute: 1, 2
- Sarah McGarrity: 
    institute: 1, 3
- Kevin Leahy: 
    institute: 1
- Jamey D. Young: 
    institute: 4
- Joseph Loscalzo: 
    institute: 1
- William M. Oldham: 
    institute: 1
    email: woldham@bwh.harvard.edu
    correspondence: true
institute:
- 1: Department of Medicine, Brigham and Women's Hospital and Harvard Medical School, Boston, MA
- 2: Department of Medicine, Massachusetts General Hospital and Harvard Medical School, Boston, MA
- 3: Center for Systems Biology, School of Health Sciences, University of Iceland, Reykjavik, Iceland
- 4: Departments of Chemical & Biomolecular Engineering and Molecular Physiology & Biophysics, Vanderbilt University, Nashville, TN
